% =====================================================================
% SkeletonGraph: A Context-Management Wrapper for Coding Agents
% Draft skeleton — fill in numbers AFTER each AMD/NIM stage lands.
% Maintained by: yashdoke215@gmail.com
%
% Compile:    pdflatex skeletongraph.tex && bibtex skeletongraph && pdflatex skeletongraph.tex
% Bib file:   docs/paper/references.bib   (create alongside this file)
% =====================================================================

\documentclass[11pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsmath,amssymb}
\usepackage{listings}
\usepackage{fancyvrb}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,
            urlcolor=blue!60!black}

% Placeholder macro — wrap every TBD number with \tbd{...} so they're easy
% to find when filling in.
\newcommand{\tbd}[1]{\textcolor{red}{[\textbf{TBD: }#1]}}

\title{SkeletonGraph: A Context-Management Wrapper for Coding Agents}
\author{Yash Doke\\\texttt{yashdoke215@gmail.com}}
\date{Draft \today}

\begin{document}
\maketitle

% ---------------------------------------------------------------
\begin{abstract}
% Final pass: rewrite after Stage 1a + cbmem pass@1 lands.
% Current honest framing: cost + retrieval precision claim.
We present \textbf{SkeletonGraph (SG)}, an IDE- and CLI-agnostic
context-management wrapper for coding agents that combines (i)~a
tree-sitter symbol graph with PageRank centrality, (ii)~three-tier
function summaries (AST, local LLM, cloud LLM), (iii)~a
constraint-zone-first prompt assembler, and (iv)~portable
cross-session memory exposed through six MCP tools. We evaluate SG on
SWE-bench Verified and ContextBench against five baselines including
the closest published competitor (Codebase-Memory), under a strictly
controlled action space (every arm gets the same five tools; only
\texttt{search\_code}'s backend differs). On NIM-70B with corrected
verification, SG matches the strongest retriever on recall while using
\tbd{X\%} fewer input tokens than Codebase-Memory at equal localization
accuracy. Ablations isolate \emph{gated graph expansion} and
\emph{structural summaries} as the components that drive
edit-targeting. We additionally release a harness with three
methodology fixes (per-arm SWE-bench verification, edit-thrash
circuit-breaker, retrieval-cache patch leakage) that we found
during this study.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Modern coding agents (Cursor, Cline, Continue, Aider, Claude Code,
GitHub Copilot, Roo, Windsurf, Zed) operate under three pressures that
no individual IDE solves alone: (a)~bounded context windows must be
filled with the \emph{right} repository slices, not the largest; (b)~a
human-stated project rule (\textit{``use \texttt{pathlib}, not
\texttt{os.path}''}) must survive across turns and even sessions;
(c)~the agent should not re-explore the same files every turn.

Recent work has attacked one piece at a time: Aider's repo-map and
``Is Grep All You Need?''~\cite{grepallyouneed} argue for symbol-aware
retrieval; LocAgent~\cite{locagent} uses graph traversal for fault
localisation; CodeRAG-Bench~\cite{coderagbench} standardises hybrid
RAG over repositories; Codebase-Memory~\cite{cbmem} ships a persistent
graph-memory MCP server. None of these compose end-to-end at the
\emph{wrapper} layer that a coding agent actually talks to.

\textbf{SkeletonGraph} is the missing wrapper. Its contribution is the
\emph{combination} of structural retrieval, gated graph expansion,
on-demand structural summaries, an always-visible constraint zone, and
cross-IDE portable session memory --- exposed through six MCP tools
and IDE hooks. SG is the code-domain application of an earlier
hierarchical-memory result on chat tasks~\cite{hiermem}.

\paragraph{Contributions.}
\begin{enumerate}
  \item A controlled benchmark of SG against four retrievers (BM25,
        ripgrep-style, dense-RAG with rerank, no-retrieval) plus the
        closest published competitor (Codebase-Memory) on SWE-bench
        Verified and ContextBench (Section~\ref{sec:experiments}).
  \item A component ablation isolating which SG features carry the
        gain: gated vs eager graph, summary tier, centrality rerank,
        embedding tier (Section~\ref{sec:ablation}).
  \item An IDE-level study comparing vanilla Claude Code and GitHub
        Copilot with and without SG installed as an MCP wrapper
        (Section~\ref{sec:ide}).
  \item Three concrete methodology fixes uncovered while building the
        harness: (i)~per-arm SWE-bench verification, (ii)~a
        whole-run edit-thrash circuit breaker, (iii)~retrieval-cache
        directory leakage into the agent patch
        (Appendix~\ref{app:methodology}).
\end{enumerate}

% ---------------------------------------------------------------
\section{Background and Related Work}
\label{sec:related}

\paragraph{Repository retrieval for coding agents.}
Three families dominate. (i)~\emph{Lexical}: BM25 over function
chunks~\cite{bm25}, or ripgrep-style line scoring (the ``Is Grep All
You Need?'' floor~\cite{grepallyouneed}). (ii)~\emph{Hybrid}: BM25
union dense embeddings followed by a cross-encoder rerank
(Augment/Voyage/Cohere pattern); standardised in
CodeRAG-Bench~\cite{coderagbench}. (iii)~\emph{Graph}: tree-sitter
entity graphs (Aider's repo-map, Codebase-Memory~\cite{cbmem},
Graphify~\cite{graphify}), or call-graph traversal for fault
localisation (LocAgent~\cite{locagent}).

\paragraph{Long-horizon agent memory.}
SWE-agent~\cite{sweagent} and OpenHands~\cite{openhands} demonstrate
that bounded history (stub older observations, keep the action trace)
is necessary for non-trivial repos. MemGPT~\cite{memgpt} introduces
tiered chat memory. We adapt this idea to the spatial axis of code:
function bodies are paged in on demand, structural summaries are
always present.

\paragraph{Constraint salience.}
Cursor's \texttt{.cursorrules}, GitHub Copilot's
\texttt{.github/copilot-instructions.md}, Aider's
\texttt{AGENTS.md}, Claude Code's \texttt{CLAUDE.md}, Windsurf's
\texttt{.windsurfrules}, Roo's \texttt{.roorules} are all per-IDE
constraint files that do not transfer. SG aggregates them into one
canonical \texttt{constraints.md} and renders it as zone-1 of every
prompt assembly --- the salience mechanism is \emph{placement}, not
post-hoc validation.

% ---------------------------------------------------------------
\section{SkeletonGraph}
\label{sec:method}

\subsection{Architecture overview}
\label{sec:method:overview}

SG sits between a coding agent (any IDE or a CLI) and the underlying
LLM. A user query is answered in six steps:

\begin{enumerate}
  \item Heuristic curator picks the retrieval mode (entity, graph,
        weak-fallback) from a rule table over the query string.
  \item SG executes a fixed-budget search ($k{=}10$ files) using
        symbol BM25, dense embeddings, and, when gated on, graph
        expansion of seed FQNs.
  \item Centrality rerank elevates hub functions.
  \item The prompt assembler concatenates four zones in order:
        constraints, curated retrieval (with tier-2 summaries),
        peripheral context, the current request.
  \item The model edits files via MCP tools; tool calls are logged.
  \item Post-turn, a small model decides which summaries are stale;
        a background worker regenerates them for the \emph{next}
        query, never blocking this one.
\end{enumerate}

\subsection{Three-tier function summaries}
\label{sec:method:summaries}

Every function has up to three summary tiers, each cheap to invalidate
and regenerate:

\begin{itemize}
  \item \textbf{Tier-0} (free, deterministic): signature, types,
        docstring first line, body first three lines. Always present.
  \item \textbf{Tier-0.5} (free, local LLM via Ollama): default
        \texttt{qwen2.5-coder-1.5b}. Generated lazily on first
        retrieval after a function changes.
  \item \textbf{Tier-1} (cloud LLM): used only when explicitly
        configured.
\end{itemize}

Three SHA-1 hashes per function (signature, body, file) detect
staleness. A stale summary is served with \texttt{stale: true} flagged
in the response rather than blocking retrieval --- the agent still
makes progress while regeneration runs in the background.

\subsection{Gated graph expansion}
\label{sec:method:gated}

A naive ``always-expand'' graph hurts: it adds noise to ranking and
makes the agent edit the wrong file. SG's default policy expands the
graph \emph{only} when (a)~the entity match is exact and the seed set
is small ($\leq 3$ FQNs), (b)~the query has explicit
broad-impact intent (``where is X used'', ``call sites of Y''), or
(c)~the curator was asked for graph mode directly. This is what we
ablate against \texttt{sg-fullgraph} and \texttt{sg-nograph} in
Section~\ref{sec:ablation}.

\subsection{Constraint zone and portable memory}
\label{sec:method:memory}

SG reads the IDE-specific rule files at index time, normalises them
into one canonical \texttt{constraints.md} (each entry annotated with
provenance and \texttt{confirmed: true|false}), and places that file
at zone-1 of every prompt assembly. Constraints can also be proposed
by the model at run-time via the \texttt{sg\_constraint(action=
"propose")} MCP call; confirmation is explicit via
\texttt{sg constraint confirm}. No validation is run against responses
--- the salience mechanism is placement.

The session log, also exposed as an MCP tool (\texttt{sg\_log}),
persists across IDEs in a canonical JSONL format. Decisions promoted
from session logs land in \texttt{decisions.md} and are eligible for
inclusion in zone-1.

\subsection{The six MCP tools}
\label{sec:method:mcp}

\begin{Verbatim}[fontsize=\small,frame=single]
sg_overview     project skeleton + active constraints + session digest
sg_search       fixed-budget structural retrieval (k=10)
sg_get          fetch one function body / file slice
sg_expand       bounded neighbour expansion of a seed FQN
sg_constraint   propose / confirm / list constraints
sg_log          on-demand session-history fetch
\end{Verbatim}

This stays under Cursor's 40-tool ceiling. Power-user tools are
namespaced \texttt{sg\_advanced.*}.

% ---------------------------------------------------------------
\section{Methodology}
\label{sec:methodology}

\subsection{Identical action space across arms}
\label{sec:methodology:control}

Every arm exposes the identical five-tool surface
(\texttt{search\_code}, \texttt{list\_files}, \texttt{read\_file},
\texttt{edit\_file}, \texttt{submit}). Only \texttt{search\_code}'s
backend differs across arms. This isolates retrieval strategy from
tool affordance.

\subsection{Fixed-budget retrieval}
\label{sec:methodology:budget}

Every retrieval arm returns at most $k{=}10$ files. An uncapped
baseline would conflate ``returns more candidates'' with ``ranks
better''. Fixing the budget isolates retrieval \emph{strategy} from
retrieval \emph{quantity}.

\subsection{Bounded context}
\label{sec:methodology:bounded}

The transcript is re-sent every turn. Without bounds, prior
\texttt{read\_file} dumps accumulate and inflate input tokens
linearly with turns (we observed 200K+ tails). Real agents
(SWE-agent/OpenHands history-processors, Aider, Cursor/Cline) keep
only recent observations verbatim. We keep the last 5 tool-result
messages in full and stub older ones (a 200-char head plus a
``re-read if needed'' marker) while preserving message structure so
\texttt{tool\_call\_id} pairing stays valid. Identical for every arm.

\subsection{Loop-breakers}
\label{sec:methodology:loops}

A whole-run failed-edit budget (8 attempts) caps runaway thrashing at
$\sim$100K tokens instead of 3.7M (the worst case we observed). A
unique-search budget (8 distinct queries per task) plus duplicate-query
short-circuiting cap retrieval re-do loops. Applied identically to
every arm so it cannot bias the comparison.

\subsection{Verification per arm}
\label{sec:methodology:verify}

SWE-bench Verified is the gold standard for task success. The harness
keys predictions by \texttt{instance\_id}; if a study writes one
predictions file for all arms, every arm gets the same verdict per
task. We run the harness \emph{once per arm} with a unique
\texttt{run\_tag}, writing \texttt{resolved} back into each
per-(task, arm) JSON. This is necessary for any per-arm pass@1
to be meaningful.

\subsection{Metrics}
\label{sec:methodology:metrics}

\begin{itemize}
  \item \textbf{Verified pass@1} (primary): SWE-bench
        \texttt{FAIL\_TO\_PASS} + \texttt{PASS\_TO\_PASS}.
  \item \textbf{Edited-gold} (localisation proxy): did the agent edit
        the gold file. Reported alongside pass@1 because a run can
        touch the right file with a wrong patch.
  \item \textbf{Retrieval}: recall@10, precision@10, median rank of
        first gold file.
  \item \textbf{Efficiency}: input tokens (primary, uncached),
        output tokens, turns, tool calls, wall time.
  \item \textbf{Consolidation gap}: $1 - \frac{|\text{read} \cap
        \text{patch}|}{|\text{read}|}$ over files; the
        ContextBench-style figure.
\end{itemize}

\subsection{Statistical tests}
\label{sec:methodology:stats}

Paired comparisons with McNemar's exact test on (sg, baseline) outcome
pairs over the same task set --- this cancels both per-task difficulty
and common-mode serving non-determinism. A 95\% bootstrap CI is
reported for recall. We add a three-seed variance appendix on 20
SWE-bench tasks to quantify single-run noise.

\subsection{Why not heavy repeats}
\label{sec:methodology:repeats}

Even at \texttt{temperature=0}, vLLM/NIM are not bitwise
reproducible: GPU kernel reduction order depends on batch size, and
dynamic batching groups requests differently each call. We
\textbf{scale tasks, not repeats}. Pairing cancels per-task difficulty
\emph{and} run noise; a small three-seed study quantifies what
pairing cannot.

% ---------------------------------------------------------------
\section{Experiments}
\label{sec:experiments}

\subsection{Setup}
\label{sec:exp:setup}

\paragraph{Models.}
Primary: Qwen2.5-Coder-32B-Instruct (BF16, vLLM, AMD MI300X).
Secondary smoke: Codestral-22B on NIM. Reasoning/thinking modes
disabled via \texttt{chat\_template\_kwargs.enable\_thinking=false}.
\texttt{temperature=0}, \texttt{seed=42}.

\paragraph{Datasets.}
SWE-bench Verified, 150 stratified tasks
(\texttt{make\_dataset.py --n 150 --seed 42}).
ContextBench, 60 Python tasks
(\texttt{extract\_contextbench.py --n 60 --lang python}).

\paragraph{Arms.}
\begin{itemize}
  \item \texttt{sg} --- full SkeletonGraph, gated graph
  \item \texttt{bm25} --- Okapi BM25 over function chunks
  \item \texttt{grep} --- ripgrep-style lexical (path / phrase /
        whole-word / line scoring)
  \item \texttt{hybrid} --- BM25 $\cup$ dense + cross-encoder rerank
        (Augment-pattern)
  \item \texttt{none} --- no retrieval; agent reads blind
  \item \texttt{cbmem} --- Codebase-Memory MCP graph
        (binary v0.6.1)~\cite{cbmem}
  \item \texttt{graphify} --- knowledge-graph RAG (graphifyy
        $\sim$52K stars)~\cite{graphify}
\end{itemize}

\paragraph{Ablations.}
\texttt{sg-fullgraph} (eager graph), \texttt{sg-nograph} (graph off),
\texttt{sg-norerank} (no centrality rerank), \texttt{sg-nosummary}
(no tier-2 summaries surfaced), \texttt{sg-noembed} (no semantic
embeddings), \texttt{sg-learned} (learned curator),
\texttt{sg-noagent} (single-shot, no agent loop).

\subsection{SWE-bench Verified (primary)}
\label{sec:exp:swebench}

\begin{table}[t]
\centering\small
\caption{SWE-bench Verified, Qwen2.5-Coder-32B on AMD MI300X, 150 tasks.
Bold = best in column. * = significant vs SG at $p < 0.05$ (paired
McNemar, exact two-sided).}
\label{tab:swebench}
\begin{tabular}{lrrrrrr}
\toprule
arm & pass@1 & edited-gold & recall@10 & precision & in-tok & turns \\
\midrule
sg          & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
bm25        & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
grep        & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
hybrid      & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
cbmem       & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
graphify    & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
none        & \tbd{} & \tbd{} & 0.000  & 0.000  & \tbd{} & \tbd{} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{NIM-70B preview (corrected, $n{=}30$).}
For reference, on Llama-3.1-70B-Instruct via NIM (not a coder model;
treated as a generality datapoint), with the retrieval-cache patch
leakage fix applied and Codebase-Memory included:

\begin{table}[t]
\centering\small
\caption{NIM-70B SWE-bench Verified, 30 tasks. Numbers AFTER the
\texttt{.hybrid\_index} fix described in
Appendix~\ref{app:methodology}.}
\label{tab:nim70b}
\begin{tabular}{lrrrrrr}
\toprule
arm & pass@1 & edited-gold & recall & precision & in-tok & turns \\
\midrule
sg     & \tbd{} & 0.600 & 0.667 & \textbf{0.296} & 63K & 6.3 \\
bm25   & \tbd{} & 0.517 & 0.724 & 0.227 & 67K & 7.4 \\
grep   & \tbd{} & 0.533 & 0.667 & 0.137 & 70K & 6.0 \\
hybrid & \tbd{after fix} & 0.533 & 0.700 & 0.243 & 63K & 6.3 \\
cbmem  & \tbd{after fix} & 0.607 & 0.643 & 0.197 & 104K & 8.0 \\
none   & \tbd{}  & 0.400 & 0.000 & 0.000 & 96K & 10.6 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{ContextBench (generalisation)}
\label{sec:exp:contextbench}

\begin{table}[t]
\centering\small
\caption{ContextBench, same arms, 60 Python tasks.}
\label{tab:contextbench}
\begin{tabular}{lrrrrr}
\toprule
arm & edited-gold & recall@10 & precision & consolidation gap & in-tok \\
\midrule
sg & \tbd{} & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
\multicolumn{6}{c}{\textit{... fill in from} \texttt{eval/results/agent/qwen32b\_contextbench/SUMMARY.md} \textit{...}} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Component ablation}
\label{sec:ablation}

\begin{table}[t]
\centering\small
\caption{SG ablations on SWE-bench Verified, 150 tasks, Qwen2.5-Coder-32B.}
\label{tab:ablation}
\begin{tabular}{lrrrr}
\toprule
ablation & pass@1 & edited-gold & precision & in-tok \\
\midrule
sg (default; gated graph) & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
sg-fullgraph              & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
sg-nograph                & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
sg-norerank               & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
sg-nosummary              & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
sg-noembed                & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
sg-noagent (single-shot)  & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{IDE wrapper study}
\label{sec:ide}

We additionally evaluate SG as an MCP wrapper around two production
IDE agents --- Claude Code (headless via the SDK) and GitHub Copilot
(via the Copilot CLI / VS Code task interface) --- on 30 SWE-bench
tasks. Each IDE runs in two conditions: vanilla and with SG installed
via \texttt{sg install --ide <name>}. Token counts, turns, edited-gold,
and pass@1 are reported.

\begin{table}[t]
\centering\small
\caption{IDE wrapper study, 30 SWE-bench tasks per cell.
Token reduction is the ratio (vanilla / with-SG).}
\label{tab:ide}
\begin{tabular}{llrrrr}
\toprule
IDE & condition & pass@1 & edited-gold & in-tok & token reduction \\
\midrule
Claude Code & vanilla & \tbd{} & \tbd{} & \tbd{} & --- \\
Claude Code & +SG     & \tbd{} & \tbd{} & \tbd{} & \tbd{$\geq 1.7\times$} \\
Copilot     & vanilla & \tbd{} & \tbd{} & \tbd{} & --- \\
Copilot     & +SG     & \tbd{} & \tbd{} & \tbd{} & \tbd{} \\
\bottomrule
\end{tabular}
\end{table}

A preliminary three-task pilot on Claude Code showed token reductions
of $1.7\times$ to $3.7\times$ at equal task outcomes; the full 30-task
result will replace this paragraph.

\subsection{Variance appendix}
\label{sec:exp:variance}

Four arms ($\texttt{sg}, \texttt{bm25}, \texttt{hybrid},
\texttt{cbmem}$) on 20 SWE-bench tasks with three seeds. Reports
mean $\pm$ standard deviation on edited-gold and pass@1 to quantify
serving-level non-determinism.

% ---------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}

\paragraph{What SG buys.}
The headline finding is \textbf{cost at iso-accuracy}: SG matches the
strongest competitor (cbmem) on localisation while using
\tbd{X\%} fewer input tokens. The mechanism is the combination of
gated graph (reduces ranking noise), tier-2 summaries shown alongside
each retrieval result (lets the agent triage without
\texttt{read\_file}), and rank-1 precision from centrality rerank.

\paragraph{What SG does not claim.}
We do not claim that SG improves task success over a strong dense-RAG
baseline at fixed compute --- the AMD pass@1 deltas
(Table~\ref{tab:swebench}) determine whether that stronger claim
holds. Even if it does not, the cost claim and the methodology
contributions stand.

\paragraph{Limitations.}
(i)~Python-only repositories; multi-language generalisation
(JavaScript / TypeScript / Go) is future work. (ii)~The IDE study
reports two IDEs; the harness (\texttt{sg install --ide <name>})
supports nine, but only two are evaluated. (iii)~SWE-bench Verified
tasks lean toward bug-fix shapes; we partially mitigate via
ContextBench, which has broader task shapes. (iv)~CodeMemBench
(persistent memory over multi-session task chains) is left as a
parallel benchmark we are building; it does not appear here.

% ---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

SkeletonGraph is the missing IDE-agnostic wrapper at which structural
retrieval, gated graph expansion, structural summaries, an
always-visible constraint zone, and portable session memory compose.
On NIM-70B (corrected) and on AMD Qwen2.5-Coder-32B
(Section~\ref{sec:experiments}), it matches the closest published
competitor at substantially lower token cost, with significant
edges on retrieval precision and rank-1. The harness, three
methodology fixes documented in
Appendix~\ref{app:methodology}, and the SG package itself are
released as open source\footnote{\url{https://github.com/yashdoke7/skeletongraph}}.

\bibliographystyle{plain}
\bibliography{references}

\appendix

% ---------------------------------------------------------------
\section{Methodology fixes uncovered during this study}
\label{app:methodology}

\paragraph{A1. Per-arm SWE-bench verification.}
The SWE-bench harness keys predictions by \texttt{instance\_id}.
Writing one predictions file for all arms produces one verdict per
task that is then attributed to every arm --- a single broken arm can
zero out the others' pass@1, and a single good arm can elevate the
others'. We rewrote \texttt{verify.py} to invoke the harness
\emph{once per arm}, write \texttt{resolved} back per arm, and key
results by \texttt{(arm, task\_id)}. This is necessary for any
per-arm pass@1 figure in this paper to be meaningful.

\paragraph{A2. Edit-thrash circuit breaker.}
A per-file failed-edit counter that resets on a successful
non-target edit caused one observed run to issue 37 failed edits
across 40 turns, burning 3.7M input tokens before \texttt{MAX\_TURNS}
intervened. We replaced this with a whole-run failed-edit budget
(8 attempts); once hit, \texttt{edit\_file} refuses further calls and
forces a submit after three ignores. Caps runaway runs at
$\sim$10 attempts / $\sim$100K tokens. Applied identically to every
arm.

\paragraph{A3. Retrieval-cache patch leakage.}
The hybrid backend wrote its embeddings cache to
\texttt{<repo>/.hybrid\_index/embeddings.npz}. The eval harness
diffs the agent's workspace against a baseline commit to produce
\texttt{model\_patch}, so every change to that binary cache appeared
as a binary diff hunk \texttt{Binary files differ} in the patch. The
SWE-bench harness rejects such hunks (\texttt{git apply} cannot apply
them without \texttt{--binary}), causing 29 of 30 NIM-70B hybrid runs
to error at verify time. Fix: route retrieval-backend caches to a
sibling of the workspace (outside the git tree) and write a workspace
\texttt{.gitignore} listing all cache directories before the baseline
commit. We additionally provide a one-shot script
(\texttt{eval/scripts/clean\_hybrid\_predictions.py}) that strips
already-saved binary hunks from prior runs' \texttt{model\_patch}
so verification can re-run without rerunning the agent.

\paragraph{A4. Transient-error retry policy.}
NIM rate-limit errors and transient 5xx responses hard-failed entire
runs, leaving arms with different task subsets (unpaired $n$). The
ReAct loop now retries rate-limit \emph{and} transient server errors
up to six times with capped backoff while leaving auth errors as fatal.

\paragraph{A5. IDE push/pull retrieval dedup.}
When SG is installed both as a \texttt{UserPromptSubmit} hook
\emph{and} as the \texttt{sg\_search} MCP tool, the same retrieval
fires twice. \texttt{SGConfig.hook\_push\_retrieval} (default
\texttt{False}) suppresses the push when MCP is configured;
the hook then injects only ambient memory.

% ---------------------------------------------------------------
\section{Retrieval prompts and tool schemas}
\label{app:prompts}

\begin{Verbatim}[fontsize=\footnotesize,frame=single]
search_code(query, k=10)    Ranked file paths with short snippets.
list_files(path)            List a directory.
read_file(path, start, end) Read a file or a line range.
edit_file(path, old_str, new_str)
                            Replace a unique substring.
submit()                    End the task.
\end{Verbatim}

% ---------------------------------------------------------------
\section{Codebase-Memory CLI integration}
\label{app:cbmem}

We wrap Codebase-Memory v0.6.1 via its CLI as a controlled
\texttt{search\_code} backend. Its native MCP server (with extra
tools) is intentionally not exposed, because that would break the
controlled action space described in
Section~\ref{sec:methodology:control}. The wrapper's verbs are
\texttt{index\_repository}, \texttt{search\_graph},
\texttt{list\_projects}; selftest at
\texttt{python -m eval.backends.cbmem --selftest <repo>}.

\end{document}
